Neural Networks Loss Landscape Convergence in Hessian Low-Dimensional Space

### 2025-05-22 slides/full/main.tex
Universal commits presents...

\begin{frame}{Neural Networks Loss Landscape Convergence in Hessian Low-Dimensional Space}
    \textbf{Goals and Tasks}
    \begin{enumerate}
        \item Study how neural network loss landscape changes with dataset size
        \item Define and measure $\Delta_k = \mathbb{E} \bigl( \cL_{k+1}(\bw) - \cL_k(\bw) \bigr)^2$
        \item Develop Hessian-based low-dimensional projection method
        \item Derive theoretical bound for $\Delta_k$ via top-$d$ eigenvalues
        \item Propose an algorithm to determine the $\Delta$-sufficient dataset size
        \item Validate threshold $k^*$ beyond which further data yield negligible change
    \end{enumerate}
\end{frame}

@@

\begin{frame}{Results and Conclusions}
    \begin{enumerate}
        \item Identified dataset thresholds \(k^*\) for MNIST and Fashion-MNIST.
        \item Loss landscape stabilizes: additional data negligible beyond \(k^*\).
        \item Hessian-based bound provides a reliable upper-bound for \(\Delta_k\).
        \item Proposed a practical algorithm for \(\Delta\)-sufficient dataset sizing.
        \item Offers guidelines for dataset collection and early stopping.
    \end{enumerate}
\end{frame}

>>>>

\begin{frame}{Neural Networks Loss Landscape Convergence in Hessian Low-Dimensional Space}
    \textbf{Goals and Tasks}
    \begin{enumerate}
        \item Study how neural network loss landscape changes with dataset size
        \item Define and measure metrics $\Delta_k$
        \item Derive theoretical bound for $\Delta_k$ via top-$d$ eigenvalues
        \item Propose an algorithm to determine the $\Delta$-sufficient dataset size
    \end{enumerate}
\end{frame}

@@

\begin{frame}{Summary}
    \begin{block}{Results}
        \begin{enumerate}
            \item Loss landscape stabilizes.
            \item Hessian-based bound provides a reliable upper-bound for \(\Delta_k\).
            \item Proposed a practical algorithm for \(\Delta\)-sufficient dataset sizing.
            \item Offers guidelines for dataset collection and early stopping.
        \end{enumerate}
    \end{block}

    \begin{block}{Future work}
    \begin{enumerate}
        \item Test the method on additional architectures.
        \item Evaluate the approach on other datasets.
        \item Incorporate automatic selection of the optimal number of Hessian eigenvalues.
    \end{enumerate}
    \end{block}
\end{frame}
